### 2017-03-19 Notes/GalileanLorentzTransformationInPhaseSpace.tex
Adding change of time units

We can define:
\begin{align*}
\bar{q} &= \hat{q} - vt \\
\bar{p} &= \hat{p} - mv \\
\bar{H} &= \frac{1}{2m} \bar{p}^2 - \frac{1}{2} mv^2 + V(\bar{q} + vt)
\end{align*}
and obtain the expected transformation. Note that the new Hamiltonian is no longer just a function of $T^*\mathcal{Q}$: it's a function of t as well.

@@

>>>>

We can define:
\begin{align*}
\bar{q} &= \hat{q} - vt \\
\bar{p} &= \hat{p} - mv \\
\bar{H} &= \frac{1}{2m} \bar{p}^2 mv^2 + V(\bar{q} + vt)
\end{align*}
and obtain the expected transformation. Note that the new Hamiltonian is no longer just a function of $T^*\mathcal{Q}$: it's a function of t as well.

@@

Let's now change the time unit.
\begin{align*}
\hat{q} &= q \\
\hat{p} &= p \\
\hat{t} &= a t \\
\end{align*}
It is canonical in the sense that $d\hat{q} \wedge d\hat{p} = dq \wedge dp$. But it does not preserve the density $\rho(\hat{q},\hat{p},\hat{t}) =\frac{1}{a} \rho(q,p,t)$. The equations of motion transform in the following way:
\begin{align*}
\frac{d\hat{q}}{d\hat{t}} &= \frac{1}{a} \frac{dq}{dt}= \frac{\partial \hat{H}}{\partial \hat{p}}= \frac{\partial \hat{H}}{\partial p} \\
\frac{d\hat{p}}{dt} &= \frac{1}{a} \frac{dp}{dt} = - \frac{\partial \hat{H}}{\partial \hat{q}} = - \frac{\partial \hat{H}}{\partial q}
\end{align*}

We have $\hat{H}= \frac{1}{a}H$. The Hamiltonian is not invariant, but rather changes as a covariant time component.
